Nested sampling with two objective functions

### 2015-12-04 Paper/ms.tex
New figure

{\bf Here is where I'll attempt to provide a justify the
algorithm}.

@@

>>>>

{\bf Here is where I'll attempt to justify the algorithm}.

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/contours.pdf}
\caption{\it The joint prior for the objective functions, and fifteen
contours of the cumulative distribution $X(L_1, L_2)$, each enclosing half
the prior mass of the previous one. \label{fig:contours}}
\end{figure}
